\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-07 main.tex
MC.

\icmltitlerunning{TUDatasets}

@@

\twocolumn[
\icmltitle{TUDataset: A collection of benchmark datasets for learning with graphs}
\icmlsetsymbol{equal}{*}

@@

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{TuDataset} for graph classification and regression. The dataset consists of over 120 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.graphlearning.io}. The experiments are fully reproducible from the code available at \url{www.github.com/chrsmrrs/tudatasets}.
\end{abstract}

@@

\paragraph{Present work.} 
Here, we give an overview of \textsc{TuDatasets}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{graphlearning.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.

@@

\section{The TUDataset collection}

The \textsc{TuDataset} contains over 120 datasets provided at \url{graphlearning.io}. The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install tudatasets}. See the website for dataset statistics and documentation.

@@

Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\cite{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\cite{Wal+2008,She+2011}, as well as several large datasets derived from the \textsc{Tox21 Challenge 2014} or \textsc{PubChem}~\cite{Kim2018}. This includes the eleven datasets from anticancer screen tests with different cancer cell lines used by~\citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns. These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells. Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{ZINC}~\cite{Dwi+2020,Jin+2018a}. For the two formers, we also provide 3D coordinates, which are crucial to study rotation-invariant GNN architectures.

@@

\xhdr{Computer vision.}
Graph-based methods are widely used in computer vision for various tasks using diverse graph models. Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}. Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3D point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\cite{Neu+2016}.

@@

\xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{TuDataset}.  Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well. See~\cref{eval} for further details and example code.

@@

\begin{table}[]\centering	
	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.2}
		\begin{tabular}{lccc}	\toprule
			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\		
			\bottomrule
	\end{tabular}}
\end{table}

\section{Experimental evaluation}

Our intent here is to provide baseline experiments and compare graph kernels and GNNs. See the appendix for detailed experimental protocal. We used the following datasets, graph kernels, and GNN baselines.

@@

\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{TUDataset} package. The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set. For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}. The number of iterations of the \textsc{$1$-WL} and \textsc{WL-OA} were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}

@@

\xhdr{GNNs.} 
For comparision with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as a neural baselines~\cite{Xu+2018}. For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK). We used mean pooling to pool the learned node embeddings to a graph embedding and used $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP. We optimized the number of hidden units from $
\{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set. Moreover, we use learning rate decay of $0.5$ with a patience parameter of $5$ with starting learning rate of $0.01$ and a minimum of $10^{-6}$. For both methods, we used the evaluation procedute described in~\cref{eval} to optimize hyperparameters and compute accuracies. See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc} and \textsc{Alchemy}.

All results can be reproduced using the scripts provided at \url{www.github.com/XXX/XXX}.

@@

We gave an overview of the \textsc{TuDataset}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data. We believe that our dataset collection will spark further progress in the area of graph represention learning, are looking forward to adding more dataset, and are excited about contributions from the community, and reseachers and practitionors from other areas.

@@

We thank everybody who provided datasets to the  \textsc{TuDataset} dataset collection.

>>>>

\icmltitlerunning{Anon}

@@

\twocolumn[
\icmltitle{\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs}
\icmlsetsymbol{equal}{*}

@@

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{\texttt{Anon}} for graph classification and regression. The dataset consists of over 120 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{Anon}. The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
\end{abstract}

@@

\paragraph{Present work.} 
Here, we give an overview of \textsc{\texttt{Anon}}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.

@@

\section{The \texttt{Anon}Dataset collection}

The \texttt{Anon} contains over 120 datasets provided at \texttt{Anon}. The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}. See the website for dataset statistics and documentation.

@@

Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\cite{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\cite{Wal+2008,She+2011}, as well as several large datasets derived from the \textsc{Tox21 Challenge 2014} or \textsc{PubChem}~\cite{Kim2018}. This includes the eleven datasets from anticancer screen tests with different cancer cell lines used by~\citet{Yan2008} to demonstrate the efficacy of classifiers based on significant graph patterns. These datasets, the largest of which contain more than 79k graphs, are typically not balanced and contain far more small molecules that are identified as inactive against cancer cells. Moreover, our collection also contain large-scale molecular regression tasks such as \textsc{Alchemy}~\cite{Che+2020}, \textsc{Qm9}~\cite{Ram+2014}, and \textsc{Zinc}~\cite{Dwi+2020,Jin+2018a}. For the two formers, we also provide 3D coordinates, which are crucial to study rotation-invariant GNN architectures.

@@

\xhdr{Computer vision.}
Graph-based methods are widely used in computer vision for various tasks using diverse graph models. Our collection provides several datasets originating from the \textsc{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}. Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3D point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{Msrc})~\cite{Neu+2016}.

@@

\xhdr{Baselines methods.} To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel in \CPP and made them accessible through the Python interface of \textsc{\texttt{Anon}}.  Moreover, all GNN architectures provided by \textsc{PyTorch Geometric} can be conveniently used as a baseline as well. See~\cref{eval} for further details and example code.

@@

\begin{table}[]\centering	
	\caption{Mean MAE (mean std. MAE, logMAE) on large-scale (multi-target) molecular regression tasks.\label{neural_short_tt}}
	\resizebox{1.0\columnwidth}{!}{\renewcommand{\arraystretch}{1.2}
		\begin{tabular}{lccc}	\toprule
			\multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{2-4}
			& {\textsc{Zinc}}     & {\textsc{alchemy}}   & {\textsc{Qm9}}   \\	\toprule
			\textsc{Gine-$\varepsilon$}    & 0.084                                                                                                                                                                                                                                     \scriptsize $\pm 0.004$   &                                                                                                                                                                                                                                0.103 {\scriptsize $\pm 0.001$} -2.956 {\scriptsize $\pm 0.029$} &  0.081 {\scriptsize $\pm 0.003$} -3.400 {\scriptsize $\pm  0.094 $}   \\
			\textsc{MPNN}    & ---                                                                                                                                                                                                                                    & --- & 0.034 {\scriptsize $\pm 0.001$} {-4.156}{\scriptsize $\pm 0.030$}  \\		
			\bottomrule
	\end{tabular}}
\end{table}		
\section{Experimental evaluation}

Our intent here is to provide baseline experiments and compare graph kernels and GNNs. We used the following datasets, graph kernels, and GNN baselines.

@@

\xhdr{Graph kernels.} As kernel baselines we used the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment} \textsc{WL-OA}~\cite{Kri+2016} included in the \textsc{\texttt{Anon}} package. The $C$-parameter was selected from $\{10^{-3}, 10^{-2}, \dotsc, 10^{2},$ $10^{3}\}$ from the validation set. For the larger datasets, we computed sparse feature vectors for each graph and used the linear $C$-SVM implementation of \text{Liblinear}~\cite{Fan+2008}. The number of iterations of the \textsc{$1$-WL} and \textsc{WL-OA} were selected from $\{0,\dotsc,5\}$.\footnote{As already shown in~\cite{She+2011}, choosing the number of iterations too large will lead to overfitting.}

@@

\xhdr{GNNs.} 
For comparison with kernel methods, we used \textsc{Gin-$\varepsilon$}~\cite{Xu+2018b} and \textsc{Gin-$\varepsilon$-JK} with jumping knowledge networks as neural baselines~\cite{Xu+2018}. For data with (continuous) edge features, we used a $2$-layer MLP to map them to the same number of components as the node features and combined them using summation (\textsc{Gine-$\varepsilon$} and \textsc{Gine-$\varepsilon$}-JK). We used mean pooling to pool the learned node embeddings to a graph embedding and used $2$-layer MLP for the final classification, using a dropout layer with $p = 0.5$ after the first layer of the MLP. We optimized the number of hidden units from $
\{ 32, 64, 128\}$, the number of layers from $ \{1, 2, 3, 4, 5\}$ using the validation set. Moreover, we use a learning rate decay of $0.5$ with a patience parameter of $5$ with a starting learning rate of $0.01$ and a minimum of $10^{-6}$. For both methods, we used the evaluation procedure described in~\cref{eval} to optimize hyperparameters and compute accuracies. See the appendix for details on the hyperparameter and evaluation protocols used for the larger molecular regression tasks, \textsc{Zinc}, \textsc{Alchemy},  \textsc{QM9}.

All results can be are reproducable using the scripts provided at \url{www.github.com/Anon}.

@@

We gave an overview of the \textsc{\texttt{Anon}}, and reported on the results of an experimental study comparing graph kernels and GNNs on a subset of the data. We believe that our dataset collection will spark further progress in graph representation learning. We are looking forward to adding more datasets and are excited about contributions from the community, researchers, and practitioners from other areas.

@@

We thank everybody who provided datasets to the  \textsc{\texttt{Anon}} dataset collection.
